---
title: "Education"
description:
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
# Education
### University of California, Irvine
- **Ph.D. in Cognitive Science** (Sep 2017 – May 2022 Expected)
  + Dissertation Title: Heart-brain Interaction during NREM Sleep Drives Sleep-dependent Memory Gains. (Advisor: Dr. Sara Mednick)
  + Dissertation Committee: Dr. Julian Thayer, Dr. Bryce Mander, Dr. Susanne Jaeggi, Dr. Greg Hickok, Dr. Aaron Bornstein

- **MS in Statistics** (Sep 2018 – June 2020)
- **DTEI Certificate in Teaching Excellence Program** (Jul – Nov 2020)
- [**DTEI Course Design Certification Program**](https://raw.githubusercontent.com/pinchunc/certificates/013665983e1a91defe6ad0d849e24c195d680b8d/CDCP.pdf) (Aug 2020)
- [**DTEI Certificate in Remote Instruction**](https://raw.githubusercontent.com/pinchunc/certificates/013665983e1a91defe6ad0d849e24c195d680b8d/CRI.pdf) (July - Aug 2020) 



```{r out.width = "60%"}
#knitr::include_graphics(here::here("img/CRI.pdf"))
```


\newpage
\newpage

### National Chengchi University
- **B.S. in Psychology** (Sep 2013 – July 2017)
- **B.Ed. in Education** (Sep 2013 – July 2017)

# Awards & Honors
- DTEI Graduate Fellowship, University of California, Irvine, 2020-2021
- Graduate Student Researcher Award, University of California, Irvine, 2017-2018
- Graduate Teaching Assistant Award, University of California, Irvine, 2018-2022
- Government Scholarship to Study Abroad, Ministry of Education, Taiwan, 2017–2019
- Conference Travel Grant, University of California, Irvine, 2018
- NVIDIA GPU Grant, NVIDIA Corporation 2017
- Student of Honor for Presidential Award, National Chengchi University, 2014-2017
- Honorary Member of the Phi Tau Phi Scholastic Honor Society, Taiwan, since 2017
- Outstanding Graduating Award, National Chengchi University, 2017 
- Dr. Fa-Mi Chen Memorial Scholarship, Taiwan, 2015